Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-08-24 parts/massmodel.tex
about mass map diagnostic

The mass maps and mass profiles are the basis of a further diagnostic:
are the mass distributions plausible?

>>>>

The mass maps and mass profiles are the basis of a further diagnostic: are 
the mass distributions plausible? This again is a judgment call by 
modellers, but it showed to be a powerful diagnostic, summarizing three 
aspects. Usually the overall shape is forced to be $180^\circ$-rotation 
symmetric and turns out plausible, but volunteers can deactivate this 
constraint. The profile slope turned out to be a good indicator for 
plausible models, as can seen by comparing the model \sw{57} to others: 
The missing core in Figure~\ref{fig:kappa} and the flat profile in 
Figure~\ref{fig:encl} disqualify this model. The clumpiness of the mass 
map is another one. Flat profile slopes can often be identified directly 
in the mass map, where the mass tiles form a checkerboard pattern.
